---
title:
author:
date:
draft: false
# tags/categories example: ["A Tag", "Another Tag"]`
tags:
categories:
#   Markdown linking is allowed, e.g. `caption: "[Image credit](http://example.org)"`.
# image path for social media
image:
#10 words or less
caption:
#default length in HUGO is 100 words
summary: 
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
## Load frequently used packages for blog posts
library('knitcitations') # for citations
library('BiocStyle') # for CRANpkg() Biocpkg() Githubpkg()
library('devtools') # for session_info()

## Load knitcitations with a clean bibliography
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')

bib <- c(
    'BiocStyle' = citation('BiocStyle'),
    'blogdown' = citation('blogdown')[2],
    'devtools' = citation('devtools'),
    'knitcitations' = citation('knitcitations')
)
```


### Post content

Typical location to start editing since the bibliography chunk is hidden. Make sure that you selected `R Markdown (.Rmd)` as the _format_ option of the post when using the `New Post` `r CRANpkg('blogdown')` addin.

### R image


```{r 'plot', echo = TRUE, fig.width = 6, fig.height = 6, eval = FALSE}
## This imaged will be saved in the /post/*_files/ directory
## Use echo = FALSE if you want to hide the code for making the plot
plot(1:10, 10:1)
```
### Custom image

The easiest option is to use the `r CRANpkg('blogdown')` _Insert Image_ RStudio addin to add an external image described in this [blog post](http://lcolladotor.github.io/2018/03/07/blogdown-insert-image-addin). You need to use version 0.5.7 or newer to have access to this plugin.

If you want to add images manually, check this [blog post](http://lcolladotor.github.io/2018/02/17/r-markdown-blog-template/#.WqChJZPwa50) for more details on the image syntax.


### Acknowledgements


This blog post was made possible thanks to:

* `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
* `r CRANpkg('blogdown')` `r citep(bib[['blogdown']])`
* `r CRANpkg('devtools')` `r citep(bib[['devtools']])`
* `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`

### References

```{r bibliography, results = 'asis', echo = FALSE, cache = FALSE}
## Print bibliography
bibliography(style = 'html')
```

### Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```
