---
title: Indiana School Enrollments 2006 to 2022
author: Rob Wiederstein
date: '2022-04-03'
slug: indiana-school-enrollments-2006-to-2022
categories:
  - R
tags:
  - leaflet
  - DT
layout: layouts/post/single
draft: TRUE
bibliography:
  - packages.bib
  - ../blog.bib
csl: ../ieee-with-url.csl
link-citations: yes
nocite: |
  @R-base, @R-blogdown, @R-tidyverse
header:
  image: ~
  alt: ~
  caption: ~
repo: ~
summary: This post examines trends in student enrollments for Indiana public schools.
---


```{r load-packages, include = F}
## Load frequently used packages for blog posts
packages <- c(
      'devtools', #for session info
      'ggthemes', #for plots
      'blogdown'
)
lapply(packages, function(x) {
  if (!requireNamespace(x)) install.packages(x)
  library(x, character.only = TRUE)
})
```

```{r set-chunk-options, include = F}
## Do not break chunk line
## Do not use spaces or periods "." or underscores "_"
## set options for knitr
knitr::opts_chunk$set(
  comment = '',
  fig.width = 6,
  fig.asp = .8,
  fig.align="center",
  message=F,
  error=F,
  warning=F,
  tidy=T,
  comment='',
  cache=T,
  dev='svg',
  echo=F
)
```


```{r write-package-bib, echo = F}
# write packages used to bib in current directory
knitr::write_bib(.packages(), "./packages.bib")
```

# [Overview](#overview)

<iframe height="800" width="100%" frameborder="no" src="https://robwiederstein.github.io/in_enrollments/"> </iframe>

(Describe the problem.)

# [Background](#background)

(Who else has worked on this problem?  What did they find?)

# [Data and model](#data)

(What data did you use, where did you get it?)

# [Results](#results)

# [Conclusion](#conclusion)

# [Acknowledgements](#acknowledge)

This blog post was made possible thanks to:

# [References](#reference)

<div id="refs"></div>

# [Disclaimer](#disclaimer)

The views, analysis and conclusions presented within this paper represent the author’s alone and not of any other person, organization or government entity. While I have made every reasonable effort to ensure that the information in this article was correct, it will nonetheless contain errors, inaccuracies and inconsistencies. It is a working paper subject to revision without notice as additional information becomes available. Any liability is disclaimed as to any party for any loss, damage, or disruption caused by errors or omissions, whether such errors or omissions result from negligence, accident, or any other cause. The author(s) received no financial support for the research, authorship, and/or publication of this article.

# [Reproducibility](#reproduce)

```{r reproducibility, echo = FALSE}
# system & package info
options(width = 120)
session_info()
```
