---
title: My Hugo Archetype for R Blogdown
author: Rob Wiederstein
date: '2021-03-06'
slug: my-hugo-archetype-for-r-blogdown
categories:
  - R
  - hugo
tags:
  - blogdown
layout: layouts/post/single
draft: no
image: ~
caption: ~
summary: By default, Hugo automatically takes the first 70 words of your content as
  its summary and stores it into the `.Summary` page variable for use in your templates.
  You may customize the summary length by setting `summaryLength` in your site configuration
  *or* you can set it in the front matter.
---


```{r load-packages, include = F}
## see http://lcolladotor.github.io/2018/03/08/blogdown-archetype-template/#.YEOC-C2cZOR
## Load frequently used packages for blog posts
x <- c(
      'devtools', #for session info
      'ggthemes', #for plots
      'knitcitations',
      'BiocStyle',
      'blogdown'
)
lapply(x, library, character.only = T)

## Load knitcitations with a clean bibliography
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')

bib <- c(
    'BiocStyle' = citation('BiocStyle'),
    'blogdown' = citation('blogdown')[2],
    'devtools' = citation('devtools'),
    'knitcitations' = citation('knitcitations')
)
```

```{r set-chunk-options, include = F}
## Do not break chunk line
## Do not use spaces or periods "." or underscores "_"
## set options for knitr
knitr::opts_chunk$set(
  comment = '',
  fig.width = 6,
  fig.asp = .8,
  fig.align="center",
  message=F,
  error=F,
  warning=F,
  tidy=T,
  comment='',
  cache=T,
  dev='svg',
  echo=F
)
```

```{r set-ggplot-theme-defaults, include = F}
#from ggthemes
library(ggplot2); theme_set(ggthemes::theme_fivethirtyeight())
```

```{r define-color-palette, include = F, eval = T}
# color blind friendly palette from http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000")
```
You can find the full code for the archetype at my [gist](https://gist.github.com/RobWiederstein/b153a853550f42c1378569b06efd49f7). Some of the code blocks were not included via `include=F` as a quick way to silence the packages loading.

## R image


```{r plot-mtcars, echo=F, fig.cap = "A plot with 538 layout theme and color blind palette."}
data(mtcars)
mtcars$cyl <- factor(mtcars$cyl)
p <- ggplot(mtcars, aes(mpg, hp, group = cyl, colour = cyl))
p <- p + scale_color_manual(values = cbPalette)
p <- p + geom_point(size = 2)
p <- p + ggtitle("mtcars")
p
```

## Custom image

The easiest option is to use the  `r CRANpkg('blogdown')` _Insert Image_ RStudio addin to add an external image.

## Overview

(Describe the problem.)

## Background

(Who else has worked on this problem?  What did they find?)

## Data and model

(What data did you use, where did you get it?)

## Results

## Conclusion

## Acknowledgements

This blog post was made possible thanks to:

* `r Biocpkg('BiocStyle')` `r citep(bib[['BiocStyle']])`
* `r CRANpkg('blogdown')` `r citep(bib[['blogdown']])`
* `r CRANpkg('devtools')` `r citep(bib[['devtools']])`
* `r CRANpkg('knitcitations')` `r citep(bib[['knitcitations']])`


## References

```{r bibliography, results = 'asis', echo = FALSE, cache = FALSE}
## Print bibliography
bibliography(style = 'html')
```

## Disclaimer

The views, analysis and conclusions presented within this paper represent the author’s alone and not of any other person, organization or government entity. While I have made every reasonable effort to ensure that the information in this article was correct, it will nonetheless contain errors, inaccuracies and inconsistencies. It is a working paper subject to revision without notice as additional information becomes available. Any liability is disclaimd as to any party for any loss, damage, or disruption caused by errors or omissions, whether such errors or omissions result from negligence, accident, or any other cause. The author(s) received no financial support for the research, authorship, and/or publication of this article.

## Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```
