---
title: Hello World Three
author: Rob Wiederstein
date: '2021-02-26'
slug: hello-world-three
categories:
  - R
tags:
  - igraph
draft: no
image: ~
caption: ~
summary: ~
---


```{r load-packages, include = F}
## Load frequently used packages for blog posts
x <- c(
      'devtools', #for session info
      'ggthemes',
      'ggplot2'
)
lapply(x, library, character.only = T)
```

```{r set-chunk-options, include = F}
## Do not break chunk line
## Do not use spaces or periods "." or underscores "_"
## set options for knitr
knitr::opts_chunk$set(
  comment = '',
  fig.width = 6,
  fig.asp = .8,
  fig.align="center",
  message=F,
  error=F,
  warning=F,
  tidy=T,
  comment='',
  cache=T,
  dev='svg',
  echo=F
)
```

```{r set-ggplot-theme, include = F}


## R image


```{r 'plot', echo = TRUE, fig.width = 6, fig.height = 6, eval = FALSE}
## This imaged will be saved in the /post/*_files/ directory
## Use echo = FALSE if you want to hide the code for making the plot
plot(1:10, 10:1)
```
## Custom image

The easiest option is to use the  _Insert Image_ RStudio addin to add an external image.
```{r}
data(mtcars)
mtcars$cyl <- factor(mtcars$cyl)
p <- ggplot(mtcars, aes(mpg, hp, group = cyl, colour = cyl))
p <- p + geom_point(size = 2)
p <- p + ggtitle("mtcars")
p

```


## Acknowledgements


## References


## Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```
