---
title: Hello World Two
author: Rob Wiederstein
date: '2021-02-26'
slug: hello-world-two
categories:
  - R
tags:
  - igraph
draft: no
image: ~
caption: ~
summary: ~
---

**Did this work?**

**And what about this?**


```{r load-packages, include = F}
## Load frequently used packages for blog posts
library('devtools') # for session_info()
```

```{r set-chunk-options, include = F}
##Do not break chunk line
##Do not use spaces or periods "." or underscores "_"
## set options for knitr
knitr::opts_chunk$set(
  comment = '',
  fig.width = 6,
  fig.asp = .8,
  fig.align="center",
  message=F,
  error=F,
  warning=F,
  tidy=T,
  comment='',
  cache=T,
  dev='svg',
  echo=F
)

```

Typical location to start editing since the bibliography chunk is hidden. Make sure that you selected `R Markdown (.Rmd)` as the _format_ option of the post when using the `New Post` addin.

## R image


```{r 'plot', echo = TRUE, fig.width = 6, fig.height = 6, eval = FALSE}
## This imaged will be saved in the /post/*_files/ directory
## Use echo = FALSE if you want to hide the code for making the plot
plot(1:10, 10:1)
```
## Custom image

The easiest option is to use the  _Insert Image_ RStudio addin to add an external image.


## Acknowledgements


## References


## Reproducibility

```{r reproducibility, echo = FALSE}
## Reproducibility info
options(width = 120)
session_info()
```
