---
title: Insert HTML Widgets in Blogdown
author: Rob Wiederstein
date: '2021-02-15'
slug: insert_htmlwidget
categories:
  - R
tags:
  - htmlwidget
  - DT
images:
  - 2021/02/15/insert_htmlwidget/leaflet-widget-embed-1200-630.jpg
description: "Blogdown & Hugo allow for the insertion of html widgets like leaflet. This is a huge time saver because one doesn't need to learn java and can instead stay within the `R` environment."
draft: false
---

There were two main reasons for moving to `blogdown`.  First, I needed a blogging platform that moved seemlessly between `R` code and its output.  It had to be easy to show the connection between the code that was used and its effect on the data. Put the two side-by-side and  people can understand what happened.  It's how I learn off the console.

The second reason was that `blogdown` offered the promise of embedding html widgets into a post.  The `htmlwidgets` package is so important in that it prevents me from having to learn java.  Don't get me wrong, java is important, but I can barely get around in `R` and want to stay focused on working with data, not learning new computer languages. This proved to be difficult, because there were no less than four hugo-themes that I tried, but kept having problems with the display in a webpage.  It was frustrating to say the least.

Not being able to embed dynamic tables into a website is a dealbreaker for me. Yes, my writing is more dependent, for example, on plots.  But a dynamic table in the modern internet world just seems to be a necessity for readers.  That's why I've started this article by using the `DT` package in placing the `mtcars` dataset into a table.  It worked!

Also, find other examples of html embeds below. For more information on the `htmlwidgets` package, see Rstudio's [page](http://www.htmlwidgets.org)


# Load Libraries

```{r load-libraries-quiet, include = F}
my.pkgs <- c("leaflet", "widgetframe", "htmlwidgets",
             "magrittr", "sigma", "DT", "ggplot2", "plotly")
lapply(my.pkgs, function(x) suppressPackageStartupMessages(library(x, character.only = T)))
```

```{r load-libraries, eval=F}
my.pkgs <- c("leaflet", "widgetframe", "htmlwidgets",
             "magrittr", "sigma", "DT", "ggplot2", "plotly")
lapply(my.pkgs, function(x) suppressPackageStartupMessages(library(x, character.only = T)))
```

# Insert Data Tables or DT Widget

```{r data-tables-widget}
# see https://rstudio.github.io/DT/
DT::datatable(iris)
```

# Insert Leaflet Widget

```{r leaflet-widget}
# https://bhaskarvk.github.io/widgetframe/
#wrap widget in <iframe> tags
m <- leaflet() %>%
  addTiles() %>%
  fitBounds(0, 40, 10, 50) %>%
  # move the center to Evansville
  setView(-87.569908, 37.975712, zoom = 15)
frameWidget(m)
```

# Insert Sigma JS

```{r sigma-widget}
data <- system.file("examples/ediaspora.gexf.xml", package = "sigma")
sigma(data)
```

# Insert Plotly Widget


```{r plotly-widget}
#https://www.htmlwidgets.org/showcase_plotly.html
p <- ggplot(data = diamonds, aes(x = cut, fill = clarity)) +
            geom_bar(position = "dodge")
ggplotly(p)
```
