---
title: Footer for Flexdashboard
author: Rob Wiederstein
date: '2021-07-05'
slug: footer-for-flexdashboard
categories:
  - R
tags:
  - flexdashboard
layout: layouts/post/single
draft: no
bibliography:
  - packages.bib
  - ../blog.bib
csl: ../ieee-with-url.csl
link-citations: yes
nocite: |
  @R-base, @R-blogdown, @R-tidyverse
header:
  image: ~
  alt: ~
  caption: ~
repo: ~
summary: By default, Hugo automatically takes the first 70 words of your content as
  its summary and stores it into the `.Summary` page variable for use in your templates.
  You may customize the summary length by setting `summaryLength` in your site configuration
  *or* you can set it in the front matter.
---


```{r load-packages, include = F}
## Load frequently used packages for blog posts
packages <- c(
      'devtools', #for session info
      'ggthemes', #for plots
      'blogdown'
)
lapply(packages, function(x) {
  if (!requireNamespace(x)) install.packages(x)
  library(x, character.only = TRUE)
})
```

```{r set-chunk-options, include = F}
## Do not break chunk line
## Do not use spaces or periods "." or underscores "_"
## set options for knitr
knitr::opts_chunk$set(
  comment = '',
  fig.width = 6,
  fig.asp = .8,
  fig.align="center",
  message=F,
  error=F,
  warning=F,
  tidy=T,
  comment='',
  cache=T,
  dev='svg',
  echo=F
)
```

```{r set-ggplot-theme-defaults, include = F}
#from ggthemes
library(ggplot2); theme_set(ggthemes::theme_fivethirtyeight())
```

```{r define-color-palette, include = F, eval = T}
# color blind friendly palette from http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000")
```

```{r write-package-bib, echo = F}
# write packages used to bib in current directory
knitr::write_bib(.packages(), "./packages.bib")
```

# [Overview](#overview)

(Describe the problem.)

# [Background](#background)

<iframe height="300" style="width: 100%;" scrolling="no" title="Bootstrap 4 Footer with Social icons" src="https://codepen.io/rob_wiederstein/embed/MWmazZq?defaultTab=html%2Cresult" frameborder="no" loading="lazy" allowtransparency="true" allowfullscreen="true">
  See the Pen <a href="https://codepen.io/rob_wiederstein/pen/MWmazZq">
  Bootstrap 4 Footer with Social icons</a> by Rob Wiederstein (<a href="https://codepen.io/rob_wiederstein">@rob_wiederstein</a>)
  on <a href="https://codepen.io">CodePen</a>.
</iframe>

# [Data and model](#data)

(What data did you use, where did you get it?)

# [Results](#results)

# [Conclusion](#conclusion)

# [Acknowledgements](#acknowledge)

This blog post was made possible thanks to:

# [References](#reference)

<div id="refs"></div>

# [Disclaimer](#disclaimer)

The views, analysis and conclusions presented within this paper represent the author’s alone and not of any other person, organization or government entity. While I have made every reasonable effort to ensure that the information in this article was correct, it will nonetheless contain errors, inaccuracies and inconsistencies. It is a working paper subject to revision without notice as additional information becomes available. Any liability is disclaimed as to any party for any loss, damage, or disruption caused by errors or omissions, whether such errors or omissions result from negligence, accident, or any other cause. The author(s) received no financial support for the research, authorship, and/or publication of this article.

# [Reproducibility](#reproduce)

```{r reproducibility, echo = FALSE}
# system & package info
options(width = 120)
session_info()
```
