---
title: Simple Features Tutorial in R
author: Rob Wiederstein
date: '2022-03-27'
slug: simple-features-tutorial-in-r
categories:
  - R
tags:
  - sf
  - leaflet
layout: layouts/post/single
draft: false
bibliography:
  - packages.bib
  - ../blog.bib
csl: ../ieee-with-url.csl
link-citations: yes
nocite: |
  @R-base, @R-blogdown, @R-tidyverse
header:
  image: ~
  alt: ~
  caption: ~
repo: ~
summary: This post is an introduction to working with the `sf` package.  "sf" is short for "simple features" and is an open source model and standard to interact with vector geometries. Downloads of the `sf` package now exceed other R packages dealing with spatial data.
---


```{r load-packages, include = F}
library(blogdown)
## Load frequently used packages for blog posts
packages <- c(
      'devtools', #for session info
      'blogdown',
      'sf',
      'leaflet'
)
lapply(packages, function(x) {
  if (!requireNamespace(x)) install.packages(x)
  library(x, character.only = TRUE)
})
```

```{r set-chunk-options, include = F}
## Do not break chunk line
## Do not use spaces or periods "." or underscores "_"
## set options for knitr
knitr::opts_chunk$set(
  comment = '',
  fig.width = 6,
  fig.asp = .8,
  fig.align="center",
  message=F,
  error=F,
  warning=F,
  tidy=F,
  comment='',
  cache=F,
  dev='svg',
  echo=F
)
```


```{r write-package-bib, echo = F}
# write packages used to bib in current directory
knitr::write_bib(.packages(), "./packages.bib")
```


# [Introduction](#overview)

This post is an introduction to working with the `sf` package.  "sf" is short for "simple features" and is an open source model and standard to interact with vector geometries. Downloads of the `sf` package now exceed other `R` packages dealing with spatial data.

The simple features [package](https://r-spatial.github.io/sf/) was first released in January, 2017. Its design and philosophy is to mirror other packages included in the "tidyverse".  Thus, manipulating data in  `sf` classed objects is similar to how it would be accomplished in `dplyr`.

Robin Lovelace is an authority in the field who has been immensely active in geospatial development for R.  He is a contributor to the `sf` package.  His book, "[Geocomputation with R](https://geocompr.robinlovelace.net/index.html)" is recommended. My first exposure to his work was a tutorial that used a previous package and his work was consulted every time I had to do a merge/join.

This post extracts portions of his book that are most commonly performed in everyday spatial analysis. An excellent [cheat sheet](https://github.com/rstudio/cheatsheets/blob/main/sf.pdf) is also available.  Two sources of data are used: the US Census Bureau county gis and USDA median income.

A

# [US Census Bureau](#CB)

The county geospatial [data]() come from the US Census.

```{r fetch-census-bureau, message = F, include = F}
#download file to local drive
url <- "https://www2.census.gov/geo/tiger/GENZ2020/shp/cb_2020_us_county_20m.zip"
destfile <- "cb_2020_us_county_20m.zip"
if(!file.exists(destfile)){download.file(url = url, destfile = destfile)}
```

```{r load-data, echo = T}
#read in file
library(sf)
#all counties
counties <- 
  sf::st_read(
    dsn = "cb_2020_us_county_20m", 
    layer = "cb_2020_us_county_20m"
    ) |>
  # convert coordinates to simple feature
  sf::st_transform('+proj=longlat +datum=WGS84') |>
  # reduce file size
	sf::st_simplify() |> 
  # convert variables to lowercase
  dplyr::rename_all(~janitor::make_clean_names(.x))
```

# [Subset to State](#subset)

Filter the dataframe to the state of interest. The result can be reached using a `dplyr` pipe.

```{r subset-to-state, echo = T}
#california fips is "06"
ca <- 
  counties |> 
  dplyr::filter(grepl("06", statefp))
```

# [Sanity Check](#sanity-check)

Before we get too much further down this rabbit hole, let's check and make sure we have something to plot. Good news!  That looks like California to me.

```{r sanity-check, echo = T}
plot(ca |> dplyr::select(countyfp))
```

# [Subset to Counties](#subset-counties)
 
```{r subset-to-counties}
ca_counties <-
  ca |> 
  dplyr::filter(name %in% c("Los Angeles", "San Francisco", "Napa")) 

library(leaflet)
  leaflet() |> 
    #setView(-120.52462403790528, 37.74238197955183, zoom = 5) |>
    fitBounds(-122.6, 32.8, -117.6, 38.8) |> 
    addTiles() |> 
    addPolygons(data = ca_counties,
                popup = ~name)
```
# [Group Counties by Dplyr](#group-counties-dplyr)

```{r group-counties-by-dplyr, echo=T}
counties_join_by_group <-
	ca |>
	dplyr::mutate(number = 1) |>
	dplyr::group_by(statefp) |>
	dplyr::summarize(tot = sum(number))
```

```{r map-counties-by-dplyr, echo = T}
#map 
leaflet() |> 
    #fitBounds(-124.4, 32.5, -114.1,  42) |> 
        setView(-120.52462403790528, 37.74238197955183, zoom = 5) |>
    addTiles() |> 
    addPolygons(data = counties_join_by_group)
```


# [Counties Join by Union](#counties-join-by-union)

The other way to join geographic subdivisions together is through the use of `sf::st_union()`.

```{r join-by-union, echo = T}
# join counties into California
counties_join_by_union <- sf::st_union(ca)
# map
leaflet() %>%
	fitBounds(-124.4, 32.5, -114.1,  42) |> 
	#base groups
	addTiles(group = "OSM (default)") |>
	addPolygons(
		data = counties_join_by_union
	)
```
# [Calculate Centroids](#centroids)

```{r centroids, echo = T}
centroids <- sf::st_centroid(ca)
leaflet() |>
	fitBounds(-122.6, 32.8, -117.6, 38.8) |> 
	#base groups
	addTiles(group = "OSM (default)") |>
	#layer groups
	addPolygons(data = sf::st_union(ca),
		    group = "State") |>
	addPolygons(data = ca,
		    group = "Counties") |>
	addMarkers(lat = unlist(lapply(centroids$geometry, "[[", 2)),
		   lng = unlist(lapply(centroids$geometry, "[[", 1)),
		   group = "Centroids"
	) |>
	#layer control
	addLayersControl(
		overlayGroups = c("State", "Counties", "Centroids"),
		position = "topright",
		options = layersControlOptions(collapsed = FALSE)
	) |>
	# hide
	hideGroup(c("State", "Counties", "Centroids"))
```

# [Merge](#merge)

Maps are commonly used as choropleth and, therefore, are often merged with data.  Here, the USDA compiles some data by county in the US.

```{r fetch-usda, echo = T, cache = T}
file <- 'https://www.ers.usda.gov/webdocs/DataFiles/48747/Unemployment.xlsx'
usda <- rio::import(
        file = file,
        skip = 4
) |> 
        dplyr::rename_all(~janitor::make_clean_names(.x)) |> 
        dplyr::select(fips_code:area_name, unemployment_rate_2020) |> 
        dplyr::filter(state == "CA") |> 
        tidyr::separate(fips_code, into = c("statefp", "countyfp"), sep = 2) |> 
        dplyr::select(statefp, countyfp, unemployment_rate_2020)
```

```{r merge-usda-uscb}
ca_choropleth <-
        dplyr::left_join(ca, usda, by = c("statefp", "countyfp"))
```

```{r map-usda-uscb, eval = T, include = T}
pal <- colorNumeric(palette = RColorBrewer::brewer.pal(5, "Dark2"),
             domain = ca_choropleth$unemployment_rate_2020
)
leaflet() |>
	fitBounds(-122.6, 32.8, -117.6, 38.8) |> 
	#base groups
	addTiles(group = "OSM (default)") |> 
        addPolygons(data = ca_choropleth,
                    color = ~pal(unemployment_rate_2020),
                    popup = ~unemployment_rate_2020)

```

# End

# [Acknowledgements](#acknowledge)

This blog post was made possible thanks to:

- Robin Lovelace

- USDA

- US Census Bureau

# [References](#reference)

<div id="refs"></div>

# [Disclaimer](#disclaimer)

The views, analysis and conclusions presented within this paper represent the author’s alone and not of any other person, organization or government entity. While I have made every reasonable effort to ensure that the information in this article was correct, it will nonetheless contain errors, inaccuracies and inconsistencies. It is a working paper subject to revision without notice as additional information becomes available. Any liability is disclaimed as to any party for any loss, damage, or disruption caused by errors or omissions, whether such errors or omissions result from negligence, accident, or any other cause. The author(s) received no financial support for the research, authorship, and/or publication of this article.

# [Reproducibility](#reproduce)

```{r reproducibility, echo = FALSE}
# system & package info
options(width = 120)
session_info()
```
